Modelling low Mach number stellar hydrodynamics with MAESTROeX

### 2019-10-01 astronum_2019_MAESTROeX/astronum-maestroex.tex
add gpu performance plot

Insert some performance plots here (do these at the hackathon?)

@@

We're currently in the process of porting \maestroex~to run on GPUs, using our experience doing the same for ~castro. This will enable us exploit the latest supercomputer architectures. So far, we've ported source terms and are in the process of porting the hydro.

>>>>

\begin{figure}\label{fig:gpu_speedup}
    \centering

    \includegraphics[width=\textwidth]{plots/gpu_speedup}

    \caption{Comparison of the performance of functions on the CPU vs the GPU. The plot shows the average execution time for several functions, recorded for a run of the 3d \texttt{reacting\_bubble} problem on Summit. Both tests were performed using a single node, with the CPU test using 42 MPI processes, each with 4 OpenMP threads, and the GPU test using 6 MPI processes, each process associated with a single GPU. Note that the $x$-axis scale is logarithmic.}

\end{figure}

@@

We're currently in the process of porting \maestroex~to run on GPUs, using our experience doing the same for \castro. This will enable us exploit the latest supercomputer architectures. So far, we've ported source terms and are in the process of porting the hydro.
